SIG Proceedings Paper in LaTeX Format

### 2019-08-28 SAC/submission/ACM_SigConf_SAC2020-2020_1.0/sample-sigconf.tex
absatract w/ word freq

\begin{document}
\title{SIG Proceedings Paper in LaTeX Format}
\titlenote{Produces the permission block, and
  copyright information}
\subtitle{Extended Abstract}
\subtitlenote{The full version of the author's guide is available as
  \texttt{acmart.pdf} document}

\author{Ben Trovato}
\authornote{Dr.~Trovato insisted his name be first.}
\orcid{1234-5678-9012}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin} 
  \state{Ohio} 
  \postcode{43017-6221}
}
\email{trovato@corporation.com}

\author{G.K.M. Tobin}
\authornote{The secretary disavows any knowledge of this author's actions.}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin} 
  \state{Ohio} 
  \postcode{43017-6221}
}
\email{webmaster@marysville-ohio.com}

\author{Lars Th{\o}rv{\"a}ld}
\authornote{This author is the
  one who did all the really hard work.}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
  \city{Hekla} 
  \country{Iceland}}
\email{larst@affiliation.org}

\author{Valerie B\'eranger}
\affiliation{%
  \institution{Inria Paris-Rocquencourt}
  \city{Rocquencourt}
  \country{France}
}
\author{Aparna Patel} 
\affiliation{%
 \institution{Rajiv Gandhi University}
 \streetaddress{Rono-Hills}
 \city{Doimukh} 
 \state{Arunachal Pradesh}
 \country{India}}
\author{Huifen Chan}
\affiliation{%
  \institution{Tsinghua University}
  \streetaddress{30 Shuangqing Rd}
  \city{Haidian Qu} 
  \state{Beijing Shi}
  \country{China}
}

\author{Charles Palmer}
\affiliation{%
  \institution{Palmer Research Laboratories}
  \streetaddress{8600 Datapoint Drive}
  \city{San Antonio}
  \state{Texas} 
  \postcode{78229}}
\email{cpalmer@prl.com}

\author{John Smith}
\affiliation{\institution{The Th{\o}rv{\"a}ld Group}}
\email{jsmith@affiliation.org}

\author{Julius P.~Kumquat}
\affiliation{\institution{The Kumquat Consortium}}
\email{jpkumquat@consortium.net}

@@

\begin{abstract}
The Skip-Gram Model with negative sampling (SGNS) is a simple and effective algorithm to create word embeddings. SGNS uses Stochastic Gradient Descent (SGD) as it's learning algorithm. While a lot of effort has gone into increasing the throughput of words of the SGNS, not much work has gone into optimizing the convergence time. Therefore, our work focuses on the latter. To achieve a better convergence time we use advanced optimizers and input shuffling as optimization techniques. Here are the components used to evaluate our work: to train our model we used the text8 dataset - to measure the quality of our word embeddings we used the wordsim353 dataset, which assess that similar words have vector represenations that are close to each other. We trained our model with multiple advanced optimizers: Momentum, Nesterov Accelerated Gradient, Adagrad, Adadelta, and Adam. We also applied input shuffling to the above optimizers. Adam combined with input shuffling outperformed every optimizer. Adam with shuffling also outperformed the current state of the art implementation Gensim. Adam converged to a similarity value of 0.66 (state of the art) in 2 epochs, while Gensim took 4 epochs. Hence, this work shows that advanced optimizers combined with input shuffling do decrease the convergence time of the SGNS. These results must be confirmed with other datasets, but optimizing our model in terms of throughput has the potential of further reducing the overall run time of the SGNS.

>>>>

\begin{document}
\title{SIG Proceedings Paper in LaTeX Format}
\titlenote{Produces the permission block, and
  copyright information}
\subtitle{Extended Abstract}

\author{Ben Trovato}
\orcid{1234-5678-9012}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin} 
  \state{Ohio} 
  \postcode{43017-6221}
}
\email{trovato@corporation.com}

\author{G.K.M. Tobin}

\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin} 
  \state{Ohio} 
  \postcode{43017-6221}
}
\email{webmaster@marysville-ohio.com}

\author{Lars Th{\o}rv{\"a}ld}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
  \city{Hekla} 
  \country{Iceland}}
\email{larst@affiliation.org}

@@

\begin{abstract}
The Skip-Gram Model with negative sampling (SGNS) is a simple and effective algorithm to create word embeddings. SGNS uses Stochastic Gradient Descent (SGD) as it's learning algorithm. While a lot of effort has gone into increasing the throughput of words of the SGNS, not much work has gone into optimizing the convergence time. Therefore, our work focuses on the latter. We propose a new batched version of the SGNS.  . Here are the components used to evaluate our work: to train our model we used the text8 dataset - to measure the quality of our word embeddings we used the wordsim353 dataset, which assess that similar words have vector represenations that are close to each other. To improve the quality of our batched version, we only allowed each word to appear once in a batch. Furthermore we deleted every word that appear more frequently than the 99 percentile. The advanced optimizer Adam combined with our batched approach outperformed the current state of the art implementation Gensim. Adam converged to a similarity value of 0.66 (state of the art) in 1 epochs, while Gensim took 4 epochs. Hence, this work shows that our batched version with advanced optimizers, and the deletion of outliers do decrease the convergence time of the SGNS. These results must be confirmed with other datasets, but optimizing our model in terms of throughput has the potential of further reducing the overall run time of the SGNS.
